%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventrynew
	{Personal Development \& Consulting}    
    {Present} 
    {}
    {Took a year off to explore the world, helping out some friends along the way:
    \vspace{4.0mm}
    \begin{cvitems}
		 \item {Built a database of 5k+ targeted B2B sales leads using a combination of web-scraping, commercial APIs, and machine learning.}
		 \item {Demystified a sales pipeline by using unstructured text profiles to predict client outcomes.}
		 \item {Automated PDF content extraction and parsing routines that will annually save hundreds of hours of tedious labor.}
      \end{cvitems}
    } 

  \cventrynew
	{Researcher at Northwestern University}    
    {2014 - 2019} 
    {Evanston, IL} 
    {Combined data science and chemical engineering to explore how cells make decisions during development, yielding publications \newline
     in \href{https://doi.org/10.1016/j.cell.2019.06.023}{\emph{Cell}} and \href{https://doi.org/10.1371/journal.pcbi.1007406}{\emph{PLOS Computational Biology}}, along with several open-source frameworks:
     \vspace{4.0mm}
      \begin{cvitems} 
		 \item {\emph{\href{https://pypi.org/project/flyqma/}{FlyQMA}}: high-throughput quantification and analysis of mosaic tissues.}         
         \item {\emph{\href{https://pypi.org/project/flyeye/}{FlyEye Analysis}}: automated inference of gene expression dynamics in the developing fly eye.}
         \item {\emph{\href{https://github.com/sebastianbernasek/binding}{TFBinding}}: statistical mechanical modeling of DNA binding site occupancy by transcription factors.}  
         \item {\emph{\href{https://github.com/sebastianbernasek/genessa}{GeneSSA}}: rapid stochastic simulation of large biochemical reaction networks.}      
      \end{cvitems}  
     \vspace{6.0mm}
    \ \newline 
    Day to day life entailed:
    \vspace{4.0mm}
     \begin{cvitems}
		 \item {Exploratory analysis of image and time series data.}
		 \item {Developing creative strategies to derive insight from noisy experiments.}
		 \item {Frequent collaboration with wet labs to design more valuable experiments.}		 
		 \item {Brainstorming \& hackathons for data-driven projects of all flavors.}
		 \item {Lots of academic reading, writing, presentations, grant writing, and peer review.}
         \item {Co-teaching undergraduate chemical engineering courses and data science bootcamps.}
         \item {Mentoring graduate, undergraduate, and high school students in formulating their own research.}         
      \end{cvitems}
     }
      
  \cventrynew
    {Process Engineer at LanzaTech} 
    {2012 - 2014} 
    {Chicago, IL} 
    {
      \begin{cvitems} 
        \item {Invented three processes for converting waste gases to lipid products. Two patents granted, one application still pending.}
		\item {Designed and built the company's core process modeling framework.}        
		\item {Identified promising technology partners, ultimately leading to major investments.}
        \item {Modeled refinery-scale processes to predict and optimize economic and life-cycle performance.}        
        \item {Advised executives and investors with technical analysis.}
      \end{cvitems}
    }
    
  \cventryshort
    {Research Assistant at UC Santa Barbara}
    {2011 - 2012}
    {Santa Barbara, CA}         
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        %\item {Modified an experimental apparatus to measure surface forces between colloidal particles.}
        \item {Conducted first ever dynamic measurement of interaction forces between vesicles. Published in \emph{Soft Matter}}        
      \end{cvitems}
    }   
  
   \cventryshort
	{Summer Intern at UL Air Quality Sciences}    
    {Summer 2011}
    {Atlanta, GA}
    {}
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Coordinated marketing effort to design a new company website.}  
%      \end{cvitems}
%    }



%---------------------------------------------------------
\end{cventries}
