%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventrynew
	{Consulting (while traveling!)}    
    {Present} 
    {}
    {
    \begin{cvitems}
		 \item {Built a database of 5k+ targeted B2B sales leads using a combination of web-scraping, commercial APIs, and machine learning.}
		 \item {Provided data-driven insight that enabled a recruiting firm to boost their monthly revenue by focusing on more probable hires.}		 
		 \item {Automated several text content extraction and parsing routines to save hundreds of hours of tedious labor.}
      \end{cvitems}
    } 

  \cventrynew
	{Researcher at Northwestern University}    
    {2014 - 2019} 
    {Evanston, IL} 
    { \begin{cvitems}	
		\item {Published in high profile journals including \href{https://doi.org/10.1016/j.cell.2019.06.023}{Cell} and \href{https://doi.org/10.1371/journal.pcbi.1007406}{PLOS Computational Biology}.}
		\item {Designed, built, and deployed several simulation and analysis frameworks for the research community.}
		\item {Discovered a surprising link between expression dynamics and metabolism by developing a model that predicts developmental mistakes.}
		\item {Discovered a novel cell decision mechanism by using computer vision to derive insight from microscopy data.}
		\item {Increased data volume and quality by developing a computer vision pipeline for automated microscopy analysis.}
	  \end{cvitems}
%     \vspace{6.0mm}
%    \ \newline 
%    \textbf{Day to day life entailed:}
%    \vspace{4.0mm}
%     \begin{cvitems}
%     	\item {Exploratory analysis and visualization of image and time series data.}     	
%     	\item {Developing creative strategies to tease insight out of noisy experiments.}   	
%     	\item {Building mathematical models to generate testable predictions.}
%		\item {Conducting tens of thousands of parallel simulations on a distributed computing cluster.}
%		\item {Frequent collaboration with wet labs to design more impactful experiments.}		 
%		\item {Brainstorming \& hackathons for data-driven projects of all flavors, from painting styles to political tweets.}
%		\item {Communicating complex ideas to diverse audiences.}
%		\item {Academic reading, writing, peer review, and grant proposals.}
%        \item {Co-teaching undergraduate chemical engineering courses and data science bootcamps.}
%        \item {Mentoring graduate, undergraduate, and high school students in formulating their own research.}         
%      \end{cvitems}
     }
     

  \cventrynew
    {Process Engineer at LanzaTech} 
    {2012 - 2014} 
    {Chicago, IL} 
    {
      \begin{cvitems}
        \item {Developed innovative renewable energy design concepts, earning two granted patents and further pending applications.}
		\item {Designed and built the company's core process modeling framework, which was rapidly adopted by all engineers.}        
		\item {Collaborated with technology providers to identify complementary value streams, leading to corporate partnerships.}
        \item {Modeled refinery-scale processes to predict and optimize economic and life-cycle performance.}        
        \item {Advised executives and investors with technical analysis that directly inspired major strategic decisions.}
      \end{cvitems}
    }
    
  \cventryshort
    {Research Assistant at UC Santa Barbara}
    {2011 - 2012}
    {Santa Barbara, CA}         
    {
      \begin{cvitems} 
        %\item {Modified an experimental apparatus to measure surface forces between colloidal particles.}
        \item {Conducted first ever dynamic measurement of interaction forces between vesicles. Published in \emph{Soft Matter}}        
      \end{cvitems}
    }   
  
%   \cventryshort
%	{Summer Intern at UL Air Quality Sciences}    
%    {Summer 2011}
%    {Atlanta, GA}
%    {}
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Coordinated marketing effort to design a new company website.}  
%      \end{cvitems}
%    }



%---------------------------------------------------------
\end{cventries}
