%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventrynew
	{Personal Development \& Consulting}    
    {Present} 
    {}
    {Took a year off to explore the world, while assisting some friends along the way:
    \vspace{4.0mm}
    \begin{cvitems}
		 \item {Built a database of 5k+ targeted B2B sales leads using a combination of web-scraping, commercial APIs, and machine learning.}
		 \item {Demystified a sales pipeline by using unstructured text profiles to predict client outcomes.}
		 \item {Automated text content extraction and parsing routines that will annually save hundreds of hours of tedious labor.}
      \end{cvitems}
    } 

  \cventrynew
	{Researcher at Northwestern University}    
    {2014 - 2019} 
    {Evanston, IL} 
    { \begin{cvitems}	
		\item {Published in high profile journals including \href{https://doi.org/10.1016/j.cell.2019.06.023}{Cell} and \href{https://doi.org/10.1371/journal.pcbi.1007406}{PLOS Computational Biology}.}
		\item {Designed, built, and deployed several simulation and analysis frameworks for the broader research community.}
		\item {Discovered a surprising link between expression dynamics and metabolism by developing a model that accurately predicts developmental mistakes.}
		\item {Discovered a novel cell decision mechanism by using computer vision and statistical analysis to derive insight from microscopy data.}
		\item {Increased data volume and quality by developing a computer vision pipeline for automated analysis of microscope images.}		
	  \end{cvitems}
     \vspace{6.0mm}
    \ \newline 
    \textbf{Day to day life entailed:}
    \vspace{4.0mm}
     \begin{cvitems}
     	\item {Exploratory analysis and visualization of image and time series data.}     	
     	\item {Developing creative strategies to tease insight out of noisy experiments.}   	
     	\item {Building mathematical models to generate testable predictions.}
		\item {Conducting tens of thousands of parallel simulations on a distributed computing cluster.}
		\item {Frequent collaboration with wet labs to design more impactful experiments.}		 
		\item {Brainstorming \& hackathons for data-driven projects of all flavors, from painting styles to political tweets.}
		\item {Communicating complex ideas to diverse audiences.}
		\item {Academic reading, writing, peer review, and grant proposals.}
        \item {Co-teaching undergraduate chemical engineering courses and data science bootcamps.}
        \item {Mentoring graduate, undergraduate, and high school students in formulating their own research.}         
      \end{cvitems}
     }
     
%		\item {A \emph{\href{https://pypi.org/project/flyqma/}{framework}} for automated analysis of mosaic imaginal discs, that lowers the barrier to high-throughput data collection.}
%		\item {A \emph{\href{https://pypi.org/project/flyeye/}{package}} for analyzing gene expression dynamics in the developing fly eye, that ascribes quantitative rigor to a popular experimental technique.}
%		\item {A \emph{\href{https://github.com/sebastianbernasek/binding}{framework}} for statistical mechanical modeling of transcription factor binding site occupancy, that leverages a novel microstate enumeration algorithm to dramatically outperform the existing state of the art in terms of both memory footprint and simulation scale.}
%		\item {A \emph{\href{https://github.com/sebastianbernasek/genessa}{framework}} for rapid stochastic simulation of large biochemical reaction networks, that outperforms all other available simulation tools for a broad class of reaction networks.}     
     
     
%      \vspace{4.0mm}
%      \begin{cvitems} 
%		 \item {}         
%         \item {}
%         \item {}  
%         \item {}      
%      \end{cvitems}  
%      
  \cventrynew
    {Process Engineer at LanzaTech} 
    {2012 - 2014} 
    {Chicago, IL} 
    {
      \begin{cvitems}
        \item {Invented three processes for converting waste gases to lipid products. One patent granted, two more applications pending.}
		\item {Designed and built the company's core process modeling framework.}        
		\item {Identified promising technology partners, ultimately leading to major investments.}
        \item {Modeled refinery-scale processes to predict and optimize economic and life-cycle performance.}        
        \item {Advised executives and investors with technical analysis.}
      \end{cvitems}
    }
    
  \cventryshort
    {Research Assistant at UC Santa Barbara}
    {2011 - 2012}
    {Santa Barbara, CA}         
    {
      \begin{cvitems} 
        %\item {Modified an experimental apparatus to measure surface forces between colloidal particles.}
        \item {Conducted first ever dynamic measurement of interaction forces between vesicles. Published in \emph{Soft Matter}}        
      \end{cvitems}
    }   
  
   \cventryshort
	{Summer Intern at UL Air Quality Sciences}    
    {Summer 2011}
    {Atlanta, GA}
    {}
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Coordinated marketing effort to design a new company website.}  
%      \end{cvitems}
%    }



%---------------------------------------------------------
\end{cventries}
